Pop-up cycleways: a peak into post COVID-19 transport futures

### 2020-05-11 conversation.Rmd
Finish draft article

<!-- Active travel has extensive [ social and environmental benefits ]. Physical activity is associated with XX health conditions….. mental health…..isolation... -->
In response to this emerging evidence, local and national transport authorities have been scrambling to ensure that walking and cycling levels can grow, while social distancing guidance is observed.
A range of interventions has been [proposed](link to academic article from USA - rl).
On Saturday 9th May, British Transport Secretary Grant Shapps announced a £2 billion investment in measures to promote walking and cycling. This follows a £10 million commitment from the Scottish Government and action announced in Wales. Hundreds of kilometres of temporary infrastructure is being put in place in dozens of cities worldwide, from [Milan] to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/) to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf). Never has there been such a need for affordable, healthy and socially distanced transport that does not create the fumes that [emerging evidence] links to coronavirus susceptibility.

>>>>

<!-- Active travel has extensive [ social and environmental benefits ]. Physical activity is associated with XX health conditions….. mental health…..isolation... -->
In response to this emerging evidence, local and national transport authorities have been scrambling to ensure that walking and cycling levels can grow, while social distancing guidance is observed.
<!-- A range of interventions has been [proposed](link to academic article from USA - rl) but it is clear that leadership, national guidance, funding and evidence on *where to invest* is needed to 'lock-in' the benefits of the nascent active transport revolution. -->
In the UK, £2 billion investment in measures to promote walking and cycling has been announced, following a £10 million package from the Scottish Government, action announced in Wales and decisive action by leaders in many other local and national authorities.
The UK package includes £250 million for "emergency interventions to make cycling and walking safer" as [Shapps put it](https://www.gov.uk/government/speeches/transport-secretarys-statement-on-coronavirus-covid-19-9-may-2020), including pop-up bike lanes, wider pavements and car-free streets.

Many pop-up interventions have already been documented internationally and in the UK and there is much to learn much from these experiences already.
There are three broad categories of pop-up interventions...
Geographically, cities with pop-up infrastructure range from [Milan] to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/) to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf). Never has there been such a need for affordable, healthy and socially distanced transport that does not create the fumes that [emerging evidence] links to coronavirus susceptibility.
